Effective Inclusion of Electronic Polarization to a Negatively Charged Membrane

### 2019-03-06 Manuscript/manuscript.tex
Update text

\usepackage[x11names]{xcolor}  % typesetting in color
%% Generate PDF/A-2u
\usepackage[a-2u]{pdfx}

@@

\usepackage{achemso}  
\usepackage{rotating}  
%\usepackage{times} 
%\usepackage{lmodern}    %% Prefer Latin Modern fonts
\usepackage{graphicx} 
\usepackage{setspace} 
\usepackage{amsmath} 
\usepackage{epstopdf} 
\usepackage{csquotes} 
\usepackage{mhchem} 
\usepackage{chemfig} 
\usepackage[obeyFinal]{easy-todo}
\usepackage[english]{babel}

@@

%% The hyperref package for clickable links in PDF and also for storing
%% metadata to PDF (including the table of contents).
%% Most settings are pre-set by the pdfx package.
\hypersetup{unicode}
\hypersetup{breaklinks=true}
\hypersetup{colorlinks,allcolors=DodgerBlue4}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
%% The manuscript does not need to include \maketitle, which is 
%% executed automatically. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\begin{document}

@@

To validate the structures of lipid bilayers, the scattering form factors and C-H bond order parameters
were calculated and compared against the experimental data as described previously~\cite{botan15,ollila16,melcr18,nmrlipids_proj4}.
%in simulations without ions were validated against NMR 
%by calculating the order parameters for the C-H bonds and against \mbox{X-ray} scattering experiments by evaluating 
%as was done in Refs.~\citenum{catte16, melcr18, nmrlipids_proj4}.
%NMR order parameters validate the structures sampled by the individual lipid molecules with atomic resolution. 
%The simulated order parameters were calculated for all C-H bonds in lipid molecules, 
%while all order paremeters in the head group and only some in the \ce{C-H} groups in tails were resolved experimentally
%(see next section and Fig.~\ref{simVSexpNOions_POPS}). 
The order parameters for each C-H bond of individual lipids in the trajectory were first averaged
over the time. Then the average over lipids was taken and the standard error of the mean of this
average was used as the error estimate of the mean \cite{botan15,ollila16,nmrlipids_proj4}.

@@

@@

We compared X-ray scattering form factors and NMR order parameters of bilayers
in pure water without any ions (or only counter ions)
from simulations and experiments. 
The experimental X-ray scattering form factors 
of a bilayer are well reproduced by ECC-POPS, 
while for Lipid17/Dang they are in a slight disagreement
(see Fig.~\ref{simVSexpNOions_POPS}). 
The agreement of Lipid17 can be improved by using different parametes for ions \cite{aqvist90},
which, however, bring other kinds of artifacts with them 
(e.g., incorrect pairing of ions, condensation at larger salt concentrations \cite{kohagen16, chen07, nmrlipids_proj4}).

>>>>

\usepackage[x11names]{xcolor}  % typesetting in color
%% Generate PDF/A-2u
%\usepackage[a-2u]{pdfx}

@@

\usepackage{achemso}  
\usepackage{rotating}  
%\usepackage{times} 
%\usepackage{lmodern}    %% Prefer Latin Modern fonts
\usepackage{graphicx} 
\usepackage{setspace} 
\usepackage{amsmath} 
\usepackage{epstopdf} 
\usepackage{csquotes} 
\usepackage{mhchem} 
\usepackage{chemfig} 
\usepackage[obeyFinal]{easy-todo}
\usepackage[english]{babel}
\usepackage{xr}
\externaldocument{manuscriptSUPPL}

@@

%% The hyperref package for clickable links in PDF and also for storing
%% metadata to PDF (including the table of contents).
%% Most settings are pre-set by the pdfx package.
%\hypersetup{unicode}
%\hypersetup{breaklinks=true}
%\hypersetup{colorlinks,allcolors=DodgerBlue4}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
%% The manuscript does not need to include \maketitle, which is 
%% executed automatically. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\begin{document}

@@

@@

The C--H bond order parameters were first averaged over the time for individual lipids and
then the standard error of the mean of the average over lipids was used as the error estimate
of the mean \cite{botan15,ollila16,nmrlipids_proj4}.

@@

The form factors from scattering and C-H bond order parameters from NMR experiments are good measures to validate
the lipid bilayer structure in MD simulations against experiments because they
are related to the bilayer dimensions (area per molecule and thickness) and
conformational fluctuations of individual lipids, respectively, and 
can be directly calculated from MD simulations~\cite{ollila16}.
The X-ray scattering form factors and C-H bond order parameters in
the headgroup and glycerol backbone region of POPS lipid bilayer are already available in the literature \cite{pan14,nmrlipids_proj4}.
Here, we extend the available experimental dataset of POPS lipids by measuring the C--H bond
order parameters also from the acyl chain region using R-PDLF experiments as described previously \cite{ferreira13}.
We first determined the order parameters of each peak corresponding different C--H bonds detected
in the first dimension (Fig. \ref{R-PDLF}) from the dipolar slices in the indirect dimension (Fig. \ref{R-PDLFslices}).
Because the exact assignment of these peaks was not possible, we assigned the
acyl chain order parameters to mimic the profile predicted by the MD simulations (Fig. \ref{simVSexpNOions_POPS}).
\todo{Tiago has to check and update this and figures in SI.}

To evaluate the effect of ECC on the structural properties of POPS lipid bilayer properties in MD simulations,
we compared the results from a simulation with original Lipid17 \cite{??} combined with the Dang ion parameters \cite{??}
with the results from ECC-POPS simulation and experiments (Fig. \ref{simVSexpNOions_POPS}).
with sodium counterions are prevously publihed
(or only counter ions)
from simulations and experiments. 
The experimental X-ray scattering form factors 
of a bilayer are well reproduced by ECC-POPS, 
while for Lipid17/Dang they are in a slight disagreement
(see Fig.~\ref{simVSexpNOions_POPS}). 
The agreement of Lipid17 can be improved by using different parametes for ions \cite{aqvist90},
which, however, bring other kinds of artifacts with them 
(e.g., incorrect pairing of ions, condensation at larger salt concentrations \cite{kohagen16, chen07, nmrlipids_proj4}).
